Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-29 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
correct the package name
update with space

# ggplot ----
plot <- ggplot(cumulative_results_w_class, 
    aes(x=outcome_names, y = estimate, group=class, color=class)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), width = 0.2) +
  scale_color_manual(name = "Disease Group", values = c("#4ac29a", "#7303c0"), 
    guide = guide_legend(direction="horizontal", title.position = "top",
                         title.hjust = 0.5)) +
  geom_hline(yintercept = 1, linetype = 2, colour = "#FF0000") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle=45, hjust = 1)) +
  ylab(expression("Cumulative odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab(NULL)

>>>>

# ggplot ----
plot <- ggplot(cumulative_results_w_class, 
    aes(x=outcome_names, y = estimate, group=class, color=class)) +
  geom_point() +
  geom_errorbar(aes(ymin=lower95, ymax=upper95), width = 0.2) +
  scale_color_manual(name = "Disease Group", values = c("#4ac29a", "#7303c0"), 
    guide = guide_legend(direction="horizontal", title.position = "top",
                         title.hjust = 0.5)) +
  geom_hline(yintercept = 1, linetype = 2, colour = "#FF0000") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    legend.position = "bottom",
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_text(angle=45, hjust = 1)) +
  ylab(expression("Cumulative odds ratio: 10 ug/m^3 increase smoke PM"[2.5])) +
  xlab("NULL")
